MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Iterative Model

### 2020-05-01 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

  #Exp--
  Exp <- RESIDUAL.SVA.GENE_EXPRESSION #as.data.frame( read.table( syn_temp$get('syn21483472')$path, header = T, sep = '\t', row.names = 1 ))
  rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
  #_# Exp_ACC <- Exp[ ,(grepl("_ACC_", colnames(Exp)))==T ]
  #_# Exp_ACC <- Exp[ ,(grepl("_PFC_", colnames(Exp)))==T ]
  Exp_temp <- Exp[ ,(grepl(paste0("_", Tissue, "_"), colnames(Exp)))==T ]
  #ID--
  ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
  table(colnames(Exp) %in% ID$RNAseq.Sample_RNA_ID )

  #_# colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_temp) ))))
  #_# colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_PFC_", "_", gsub( "PFC_BP_", "", colnames(Exp_temp) ))))
  if( Tissue == 'PFC' ){
    colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_PFC_", "_", gsub( "PFC_BP_", "", colnames(Exp_temp) ))))
  }else{
    if( Tissue == 'ACC' ){
      colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_temp) ))))
    }else{
      warning('Inproper Tissue Specified')
    }
  }
  Exp <- Exp_temp
  #Sync Names
  Padder <- function( names ){
    #'@names format of 'CMC_PITT_XXXX' ie colnames(Exp)
    foo <- do.call( rbind, strsplit(names, '_'))
    foo[,3] <- str_pad(foo[,3], 5, pad = "0")
    return( paste0(foo[,1], "_", foo[,2], "_", foo[,3] ) )
  }
  colnames(Exp) <- Padder( colnames(Exp) )
  colnames(Impute) <- Padder( colnames(Impute) )

@@

  setEPS()
  #postscript( paste0( Tissue, "_Val.eps" ), onefile = TRUE)
    #ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
      #geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
      #theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") 
  #dev.off()

  ggsave( filename=Tissue, "_Val.eps",
    plot = ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
      geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
      theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") ,
    device = "pdf",
    path = NULL,
    scale = 1,
    width = 14,
    height = 7,
    units = "in",
    dpi = 300,
    limitsize = TRUE
  )

@@

#Upload Plots:
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.eps', name = 'LogP value as a function of correlation for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

@@

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Val.eps', name = 'LogP value as a function of correlation for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

>>>>

  #Exp--
  Exp <- RESIDUAL.SVA.GENE_EXPRESSION #as.data.frame( read.table( syn_temp$get('syn21483472')$path, header = T, sep = '\t', row.names = 1 ))
  rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
  Exp_temp <- Exp[ ,(grepl(paste0("_", Tissue, "_"), colnames(Exp)))==T ]
  #ID--
  ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
  table(colnames(Exp) %in% ID$RNAseq.Sample_RNA_ID )

  if( Tissue == 'PFC' ){
    colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_PFC_", "_", gsub( "PFC_BP_", "", colnames(Exp_temp) ))))
  }else{
    if( Tissue == 'ACC' ){
      colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_temp) ))))
    }else{
      warning('Inproper Tissue Specified')
    }
  }
  Exp <- Exp_temp
  #Sync Names
  Padder <- function( names ){
    #'@names format of 'CMC_PITT_XXXX' ie colnames(Exp)
    foo <- do.call( rbind, strsplit(names, '_'))
    foo[,3] <- str_pad(foo[,3], 5, pad = "0")
    return( paste0(foo[,1], "_", foo[,2], "_", foo[,3] ) )
  }
  colnames(Exp) <- Padder( colnames(Exp) )
  colnames(Impute) <- Padder( colnames(Impute) )

@@

  ggsave( filename=paste0( Tissue, "_Val.pdf" ),
    plot = ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
      geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
      theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") ,
    device = "pdf",
    path = NULL,
    scale = 1,
    width = 14,
    height = 7,
    units = "in",
    dpi = 300,
    limitsize = TRUE
  )

@@

#Upload Plots:
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.pdf', name = 'LogP value as a function of correlation for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

@@

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Val.pdf', name = 'LogP value as a function of correlation for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
